---
title: "Analysis"
author: "Rob van der Wielen"
date: "2023-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#--- Libraries and packages ---#
```{r}
install.packages("vtable")
library(vtable)
```

#--- Loading datasets ---#

```{r}
# Load in data set
all_platforms_cleaned <- read.csv("C:/Users/Systeembeheer/OneDrive - Tilburg University/Documenten/Master/Marketing Analytics/Thesis/ThesisRob/ThesisRob/Datasets/Cleaned_data/all_platforms_cleaned.csv", sep = ",", na.strings=c("", "NA"))
summary(all_platforms_cleaned)

# Load in data set
netflix_data_complete <- read.csv("C:/Users/Systeembeheer/OneDrive - Tilburg University/Documenten/Master/Marketing Analytics/Thesis/ThesisRob/ThesisRob/Datasets/Cleaned_data/netflix_data_complete.csv", sep = ",", na.strings=c("", "NA"))
summary(netflix_data_complete)
```

#--- Removing NA ---#

*Somehow in the all platforms data set there are still three rows with NAs. These are removed from the data set*
```{r}
#removing NA
all_platforms_cleaned <- all_platforms_cleaned %>%
  select(c(2:10, 38:44)) 
all_platforms_cleaned <- all_platforms_cleaned %>%
  select(!c(rank, cumulative_rank, week_num)) %>%
  distinct()

```

#--- Frequency statistics ---#

```{r}
number_platforms <- all_platforms_cleaned %>% 
  group_by(platform) %>% 
  summarize(count = n()) %>% 
  arrange(count) %>%
  distinct()
```

```{r}
# dummy code genre
all_platforms_cleaned <- all_platforms_cleaned %>% separate_rows(genre, sep = ',') %>% mutate(val = 1) %>% 
  pivot_wider(names_from = genre, values_from = val, values_fill = list(val = 0)) 
head(all_platforms_cleaned)
  
all_platforms_cleaned <- all_platforms_cleaned %>%
  select(!21)

# join the two data frames together
# Transform data set to wider format 
Genre_columns <- paste("genre_", colnames(all_platforms_cleaned[13:20]))
Genre_columns <- sub(" ", "", Genre_columns)

colnames(all_platforms_cleaned)[13:20] <- Genre_columns


```

```{r}
# Create a table of count of titles by genre
genre_count <- all_platforms_cleaned %>% 
  gather(key = "genre", value = "dummy", starts_with("genre_")) %>% 
  filter(dummy == 1) %>% 
  select(!dummy) %>% 
  group_by(genre) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  arrange(desc(count))

# Create a table of count of titles by platform, and genre. Also filtering only the top 10 most occurring genres across all platforms to make it not to long. 
genre_count_by_platform <- all_platforms_cleaned %>% 
  gather(key = "genre", value = "dummy", starts_with("genre_")) %>% 
  filter(dummy == 1) %>% 
  select(!dummy) %>% 
  group_by(genre, platform) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  filter(genre %in% genre_count$genre)

# Create a table of count of titles by platform, and MPAA rating. Also filtering only the top 10 most occurring genres across all platforms to make it not to long. 
mpaa_count_by_platform <- all_platforms_cleaned %>% 
  gather(key = "mpaa", value = "dummy", starts_with("mpaa_")) %>% 
  filter(dummy == 1) %>% 
  select(!dummy) %>% 
  group_by(mpaa, platform) %>% 
  summarize(count = n()) %>% 
  ungroup()

```


```{r}
# Transform data set to wider format 
platforms_wider_genre <- genre_count_by_platform %>%
  pivot_wider(names_from = platform, values_from = count) %>%
  rename(genre, genre_mpaa = genre)


# Transform data set to wider format
platforms_wider_mpaa <- mpaa_count_by_platform %>%
  pivot_wider(names_from = platform, values_from = count) %>%
  rename(mpaa, genre_mpaa = mpaa)
```

```{r}
# join the two data frames together
all_platforms_genre_mpaa <- rbind(platforms_wider_genre, platforms_wider_mpaa)
```

```{r}
#Write to csv file
write.csv(all_platforms_genre_mpaa, "all_platforms_genre_mpaa.csv")
```


#--- Summary statistics ---#
*The formatting of the table will be done in MS Word*
```{r}
#creating summary statistics file
st(netflix_data_complete,
         summ = list(
     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)')),
   summ.names = list(
     c('N','Mean','SD','Min','Max')), digits = 2, numformat = NA, file='descriptive_statistics')
```


# Mean cumulative rank per video Type
```{r}
netflix_data_complete %>%
  group_by(Type) %>%
  summarize(test = mean(cumulative_rank))
```

# Sequel per type 
```{r}
netflix_data_complete %>%
  group_by(Type, sequel) %>%
  count()
```

# Number of exclusives
```{r}
netflix_data_complete %>%
  group_by(exclusive) %>%
  count()
```

# Creating a boxplot for the cumulative rank splits up by type
```{r}
dir.create("C:/Users/Systeembeheer/OneDrive - Tilburg University/Documenten/Master/Marketing Analytics/Thesis/ThesisRob/ThesisRob/R_scripts/plots")

pdf("plots/boxplot_type.pdf") 
# create separate dataframes for movies and TV shows
movies <- subset(netflix_data_complete, Type == 1)
tv_shows <- subset(netflix_data_complete, Type == 0)

# create a boxplot with two plots
par(mfrow = c(2, 1))
boxplot(movies$cumulative_rank, horizontal =TRUE, ylim = c(0, 20), ylab = "Movies") 
boxplot(tv_shows$cumulative_rank, horizontal = TRUE, ylim = c(0, 20), sub = "Cumulative weeks", ylab = "TV-shows")
dev.off() 

```


